A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Fix threats

\section{Threats to Validity}
The primary threat to validity is the issue of code coverage, a cause of concern
for any dynamic approach. We mitigate this by including only those R packages in
our corpus that have many reverse dependencies and thus high code coverage.
Secondly, we turn off the bytecode compiler for this study. The bytecode
compiler can also call eval. Thirdly, we do not get source locations for
\UndefinedEvalsRnd eval calls. These are the calls in which eval is passed as an
argument to a higher-order functions or is defined in a function returned by a higher-order function and the R parser does not retain location
information for them. However, this is a meager \PercentUndefinedEval of all eval
calls and is unlikely to affect our analysis.

>>>>

\section{Threats to Validity} The primary threat to validity is the issue of
code coverage, a cause of concern for any dynamic approach. We mitigate this by
including only those R packages in our corpus that have many reverse
dependencies and thus high code coverage. Secondly, we turn off the bytecode
compiler for this study. The bytecode compiler can also call eval. Thirdly, we
do not get source locations for \UndefinedEvalsRnd eval calls. In these cases
\eval is either passed as an argument to a higher-order functions or is defined
in a function returned by a higher-order function and the R parser does not
retain location information for \eval. However, this is a meager
\PercentUndefinedEval of all eval calls and is unlikely to affect our analysis.
